---
title: "P8105_hw1_yw4667"
output: github_document
date: "2025-09-13"
---

```{r setup, include = FALSE}
library(moderndive)
library(tidyverse)
data("early_january_weather")
```

# Problem 1

## Short Description of the Dataset

The `early_january_weather` dataset contains weather data from EWR airport for early January 2013. 

The variables in this dataset are: `r names(early_january_weather)`. 

Important variables are as below:

`time_hour`: date and time of each observation

`temp`: temperature in degrees Fahrenheit

`humid`: relative humidity as a percentage

`dewp`: dewpoint temperature(in degrees of Fahrenheit)

`wind_speed`: wind speed in miles per hour

`origin`: weather station identifier

The size of the dataset is `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean temperature is `r round(mean(early_january_weather$temp, na.rm = TRUE), 2)` degrees Fahrenheit.

## Scatterplot of Temperature vs Time_Hour

```{r yx_scatter}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
   labs(
    title = "Early January weather in 2013:Temperature vs Time",
    x = "Time",
    y = "Temperature (°F)",
    color = "Humidity (%)"
  )
```

## Description of Patterns

Several patterns of this scatter plot are as blow:

1. **Daily temperature cycles**: There are clear daily fluctuations in temperature, with cooler temperatures occurring during the night and warmer temperatures during the day.

2. **Overall warming trend**: There appears to be a gradual increase in temperatures over the time period shown.

3. **Humidity patterns**: Higher humidity levels (lighter colored dots) tend to occur with moderate temperatures, while extreme temperatures often correspond to lower humidity levels(darker colored dots).

## Export the scatterplot

```{r save_plot}
ggsave("temp_vs_time_scatterplot.png")
```

# Problem 2
